---
title: "Connectome Analysis"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(car)
library(ggplot2)
library(psych)
library(lm.beta)
library(mice)

setwd("C:/Users/ddcc2/OneDrive/Desktop/Connectome Analysis/")

# Three different data sets for freesurfer, behavioral and dempgraphic data. Combine data into one data frame
behave=read.csv("behave_connectome.csv")
freesurf=read.csv("freesurf_connectome.csv")
demographic=read.csv("demographic.csv")
dat=cbind(behave,demographic)
'''

#Doesn't appear to be too much multicolinearity among these predictors
```{r}
# Scatterplot to look at associations
scatterplotMatrix(~Endurance_Unadj+BMI+Age_in_Yrs+Gender+SSAGA_Educ+BPSystolic,id=list(n=3), data=dat)
require(HH)

# Check for multicolinearity
mod1 <- lm(Endurance_Unadj~BMI+Age_in_Yrs+Gender+SSAGA_Educ+BPSystolic, data=dat, x=TRUE)
lm.beta(mod1)
summary(mod1)
vif(mod1)

sqrt(vif(mod1))

tol<-1/vif(mod1); tol

# look at residuals
qqPlot(mod1)
residualPlots(mod1)

# Scatterplot of some diffusion data
scatterplotMatrix(~Endurance_Unadj+l_CA1_ODI+l_CA1_NDI+r_CA1_ODI+r_CA1_NDI,id=list(n=3), data=dat)

# Check residuals
mod1 <- lm(Endurance_Unadj~l_CA1_ODI+l_CA1_NDI+r_CA1_ODI+r_CA1_NDI, data=dat, x=TRUE)
lm.beta(mod1)
summary(mod1)
qqPlot(mod1)
residualPlots(mod1,id=list(n=3))

summary(mod1)
residualPlot(mod1, id=list(n=3))

stud.resid<-rstudent(mod1)
stud.resid.df<-data.frame(ID=(dat$Subject),studres=stud.resid)
outlierTest(mod1)
influencePlot(mod1, main="", id=list(n=3))

# Look for influential/outlier points
infIndexPlot(mod1, main="", 
vars=c("Cook"), 
id=list(n=4))
```

## Fitness and Cognition Controlling for nothing (Split up gender in graphs)
# There appear to be associations

```{r}
# Flanker (Executive)
mod1=lm(dat$Flanker_Unadj~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)
ggplot(data=behave, aes(x=Endurance_Unadj,y=Flanker_Unadj,color=Gender))+geom_point()+geom_smooth(method="lm")

# Pic Vocab
mod2=lm(dat$PicVocab_Unadj~dat$Endurance_Unadj)
summary(mod2)
lm.beta(mod2)
ggplot(data=behave, aes(x=Endurance_Unadj,y=PicVocab_Unadj,color=Gender))+geom_point()+geom_smooth(method="lm")

# Pic Sequence (Episodic)
mod2=lm(dat$PicSeq_Unadj~dat$Endurance_Unadj)
summary(mod2)
lm.beta(mod2)
ggplot(data=behave, aes(x=Endurance_Unadj,y=PicSeq_Unadj,color=Gender))+geom_point()+geom_smooth(method="lm")

# Card sort (Executive)
mod3=lm(dat$CardSort_Unadj~dat$Endurance_Unadj)
summary(mod3)
lm.beta(mod3)
ggplot(data=behave, aes(x=Endurance_Unadj,y=CardSort_Unadj,color=Gender))+geom_point()+geom_smooth(method="lm")

# Penn progressive matrices (Fluid Intelligence)
mod3=lm(dat$PMAT24_A_CR~dat$Endurance_Unadj)
summary(mod3)
lm.beta(mod3)
ggplot(data=behave, aes(x=Endurance_Unadj,y=PMAT24_A_CR,color=Gender))+geom_point()+geom_smooth(method="lm")


# Processing speed (Pattern completion speed)
mod6=lm(dat$ProcSpeed_Unadj~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
ggplot(data=behave, aes(x=Endurance_Unadj,y=ProcSpeed_Unadj,color=Gender))+geom_point()+geom_smooth(method="lm")

# Self Regulation/Impulsivity (Delay Discounting)
mod6=lm(dat$DDisc_AUC_200~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
ggplot(data=behave, aes(x=Endurance_Unadj,y=DDisc_AUC_200,color=Gender))+geom_point()+geom_smooth(method="lm")

# Spatial Orientation
mod6=lm(dat$VSPLOT_TC~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
ggplot(data=behave, aes(x=Endurance_Unadj,y=VSPLOT_TC,color=Gender))+geom_point()+geom_smooth(method="lm")

# Penn Word Memory (Episodic memory)
mod6=lm(dat$IWRD_TOT~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
ggplot(data=behave, aes(x=Endurance_Unadj,y=IWRD_TOT,color=Gender))+geom_point()+geom_smooth(method="lm")

# Working Memory (list sorting)
mod6=lm(dat$ListSort_Unadj~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
ggplot(data=behave, aes(x=Endurance_Unadj,y=ListSort_Unadj,color=Gender))+geom_point()+geom_smooth(method="lm")

# Global Cognition
mod8=lm(dat$CogTotalComp_Unadj~dat$Endurance_Unadj)
summary(mod8)
lm.beta(mod8)
ggplot(data=behave, aes(x=Endurance_Unadj,y=CogTotalComp_Unadj,color=Gender))+geom_point()+geom_smooth(method="lm")
```
##Fitness and Cognition basic regression model and then model controlling for age, gender, education, systolic blood pressure and BMI
# Includes residual plots and standardized values
# Seems like fitness is still significant for a lot of the measures even after controlling for the additional facotrs.
```{r}
# Flanker (Executive)
mod1=lm(dat$Flanker_Unadj~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)
mod1=lm(dat$Flanker_Unadj~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Pic Vocab
mod2=lm(dat$PicVocab_Unadj~dat$Endurance_Unadj)
summary(mod2)
lm.beta(mod2)
mod1=lm(dat$PicVocab_Unadj~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Pic Sequence (Episodic)
mod2=lm(dat$PicSeq_Unadj~dat$Endurance_Unadj)
summary(mod2)
lm.beta(mod2)
mod1=lm(dat$PicSeq_Unadj~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Card sort (Executive)
mod3=lm(dat$CardSort_Unadj~dat$Endurance_Unadj)
summary(mod3)
lm.beta(mod3)
mod1=lm(dat$CardSort_Unadj~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Penn progressive matrices (Fluid Intelligence)
mod3=lm(dat$PMAT24_A_CR~dat$Endurance_Unadj)
summary(mod3)
lm.beta(mod3)
mod1=lm(dat$PMAT24_A_CR~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)



# Processing speed (Pattern completion speed)
mod6=lm(dat$ProcSpeed_Unadj~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
mod1=lm(dat$ProcSpeed_Unadj~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Self Regulation/Impulsivity (Delay Discounting)
mod6=lm(dat$DDisc_AUC_200~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
mod1=lm(dat$DDisc_AUC_200~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Spatial Orientation
mod6=lm(dat$VSPLOT_TC~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
mod1=lm(dat$VSPLOT_TC~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Penn Word Memory (Episodic memory)
mod6=lm(dat$IWRD_TOT~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
mod1=lm(dat$IWRD_TOT~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Working Memory (list sorting)
mod6=lm(dat$ListSort_Unadj~dat$Endurance_Unadj)
summary(mod6)
lm.beta(mod6)
mod1=lm(dat$ListSort_Unadj~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Global Cognition
mod8=lm(dat$CogTotalComp_Unadj~dat$Endurance_Unadj)
summary(mod8)
lm.beta(mod8)
mod1=lm(dat$CogTotalComp_Unadj~dat$BMI+dat$Endurance_Unadj+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ+dat$BPSystolic)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)

```

## Hippocampus Subfields and Endurance
# Basic Regression and then Control
# Includes standardized coefficients and general and residual plots

```{r}
# Left Hipp CA1
# ODI
mod1=lm(dat$l_CA1_ODI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=l_CA1_ODI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$l_CA1_ODI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


#NDI
mod1=lm(dat$l_CA1_NDI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=l_CA1_NDI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$l_CA1_NDI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Right Hipp CA1
# ODI
mod1=lm(dat$r_CA1_ODI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=r_CA1_ODI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$r_CA1_ODI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


#NDI
mod1=lm(dat$r_CA1_NDI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=r_CA1_NDI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$r_CA1_NDI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)

# Left Hipp CA3
# ODI
mod1=lm(dat$l_CA3_ODI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=l_CA3_ODI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$l_CA3_ODI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


#NDI
mod1=lm(dat$l_CA3_NDI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=l_CA3_NDI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$l_CA3_NDI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Right Hipp CA3
# ODI
mod1=lm(dat$r_CA3_ODI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=r_CA3_ODI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$r_CA3_ODI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


#NDI
mod1=lm(dat$r_CA3_NDI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=r_CA3_NDI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$r_CA3_NDI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)

# Left Hipp CA4DG
# ODI
mod1=lm(dat$l_CA4DG_ODI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=l_CA4DG_ODI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$l_CA4DG_ODI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


#NDI
mod1=lm(dat$l_CA4DG_NDI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=l_CA4DG_NDI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$l_CA4DG_NDI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


# Right Hipp CA4DG
# ODI
mod1=lm(dat$r_CA4DG_ODI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=r_CA4DG_ODI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$r_CA4DG_ODI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)


#NDI
mod1=lm(dat$r_CA4DG_NDI~dat$Endurance_Unadj)
summary(mod1)
lm.beta(mod1)

ggplot(data=behave, aes(x=Endurance_Unadj,y=r_CA4DG_NDI,color=Gender))+geom_point()+geom_smooth(method="lm")

mod1=lm(dat$r_CA4DG_NDI~dat$Endurance_Unadj+dat$Gender+dat$Age_in_Yrs+dat$SSAGA_Educ+dat$BMI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$Endurance_Unadj)

```

# Hippocampus and Cognition
# Control for BMI, age, gender, and education
# Basic and full model with standardized coefficients, general graph and residualized plot.
```{r}
# Left Hipp CA1
# ODI

mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA1_ODI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA1_ODI)

mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA1_ODI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA1_ODI)


#NDI
mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA1_NDI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA1_NDI)

mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA1_NDI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA1_NDI)


# Right Hipp CA1
# ODI
mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA1_ODI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA1_ODI)

mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA1_ODI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA1_ODI)


#NDI
mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA1_NDI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA1_NDI)

mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA1_NDI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA1_NDI)


# Left Hipp CA3
# ODI
mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA3_ODI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA3_ODI)

mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA3_ODI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA3_ODI)


#NDI
mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA3_NDI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA3_NDI)

mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA3_NDI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA3_NDI)


# Right Hipp CA3
# ODI
mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA3_ODI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA3_ODI)

mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA3_ODI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA3_ODI)


#NDI
mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA3_NDI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA3_NDI)

mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA3_NDI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA3_NDI)

# Left Hipp CA4DG
# ODI
mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA4DG_ODI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA4DG_ODI)

mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA4DG_ODI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA4DG_ODI)


#NDI
mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA4DG_NDI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA4DG_NDI)

mod1=lm(dat$CogTotalComp_Unadj~dat$l_CA4DG_NDI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$l_CA4DG_NDI)


# Right Hipp CA4DG
# ODI
mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA4DG_ODI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA4DG_ODI)

mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA4DG_ODI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA4DG_ODI)


#NDI
mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA4DG_NDI)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA4DG_NDI)

mod1=lm(dat$CogTotalComp_Unadj~dat$r_CA4DG_NDI+dat$BMI+dat$Age_in_Yrs+dat$Gender+dat$SSAGA_Educ)
summary(mod1)
lm.beta(mod1)
avPlot(mod1,dat$r_CA4DG_NDI)
```
